Dataflow-Guided Filtering for Efficient and Adjustable Run-Time Monitoring

### 2014-05-30 introduction.tex
Update numbers in intro/abstract.

% Evaluation
In order to evaluate our approach, we applied it to 3 different monitoring
techniques. These monitoring techniques vary in what events they monitor, the
size and semantics of their metadata, and the operations performed on metadata.
Our experiments show that with 10\% overheads, we can still provide 49-90\% of
coverage on average depending on the monitoring technique. By increasing the
overhead budget, the coverage rate can be increased. Our architecture is able
to closely meet the specified budgets. For all but one benchmark, the overheads
seen were within 2\% of the target overhead. Our results show that X policy is
able to achieve very close overhead matching (within X\% on average) with an
average coverage of X\%. On the other hand, by using Y policy, the overhead
matching is not as high (within Y\% on average) but average coverage increases
to (Y\%).

>>>>

% Evaluation
In order to evaluate our approach, we applied it to 3 different monitoring
techniques. These monitoring techniques vary in what events they monitor, the
size and semantics of their metadata, and the operations performed on metadata.
Our experiments show that filtering reduces the average overhead of these
monitors from 7-18x down to 13-300\%.
In addition, with partial monitoring, for the monitoring schemes which still
see average overheads of 300\%, we show that with just 50\% overheads, we can still
provide 51-83\% of coverage on average. By increasing the
overhead budget, this coverage rate can be increased.

### 2014-05-30 title.tex
Update numbers in intro/abstract.

Recent studies have proposed various parallel run-time monitoring techniques to
improve the reliability, security, and debugging capabilities of computer
systems. However, these run-time monitors can introduce large performance and energy
overheads, especially when performed on programmable cores.
%Traditionally, these overheads have been an
%all-or-nothing cost; monitoring cannot be used if the overheads are considered
%too large.  
In this paper, we introduce a hardware dataflow tracking engine that can be
used to filter out unnecessary monitoring and enable adjustable partial monitoring.
The dataflow engine can identify events with null metadata so that they can
be filtered out. To further reduce the overhead of monitoring, we propose
to enable a trade-off between monitoring coverage and overhead by dropping certain
monitoring operations. For this partial monitoring, the dataflow engine is used
to track dropped monitoring flows so that false positives can be avoided.
Given the architecture, we also investigate how the dropping decisions should be
made for partial monitoring and show that there exists a trade-off between closely
matching an overhead target and the coverage that can be achieved.
% Our experiments show that the system is able to
% closely meet the target overhead and achieve significant monitoring coverage
% for reasonable overhead targets.
The experimental results show that filtering can significantly reduce monitoring
overheads from XX\%-XX\% on average, depending on the monitoring scheme, to
XX\%-XX\%. Additionally, the partial monitoring is shown to still achieve XX\% coverage 
only with a 10\% overhead target.

>>>>

Recent studies have proposed various parallel run-time monitoring techniques to
improve the reliability, security, and debugging capabilities of computer
systems. However, these run-time monitors can introduce large performance and energy
overheads, especially when performed on programmable cores.
%Traditionally, these overheads have been an
%all-or-nothing cost; monitoring cannot be used if the overheads are considered
%too large.  
In this paper, we introduce a hardware dataflow tracking engine that can be
used to filter out unnecessary monitoring and enable adjustable partial monitoring.
The dataflow engine can identify events with null metadata so that they can
be filtered out. To further reduce the overhead of monitoring, we propose
to enable a trade-off between monitoring coverage and overhead by dropping certain
monitoring operations. For this partial monitoring, the dataflow engine is used
to track dropped monitoring flows so that false positives can be avoided.
Given the architecture, we also investigate how the dropping decisions should be
made for partial monitoring and show that there exists a trade-off between closely
matching an overhead target and the coverage that can be achieved.
% Our experiments show that the system is able to
% closely meet the target overhead and achieve significant monitoring coverage
% for reasonable overhead targets.
The experimental results show that filtering can significantly reduce monitoring
overheads from 7x-18x on average, depending on the monitoring scheme, to
13\%-300\%. Additionally, for the monitoring schemes which still show 300\%
average overhead, partial monitoring can reduce this overhead to 50\% while
still achieving 51-83\% average monitoring coverage.
